---
title: "Assignment 7"
author: "MG"
date: "10/10/2020"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(RCurl)
library(XML)
library(jsonlite)

```

## Week 7 Working with XML and JSON in R

Our assignment this week is the choose 3 books (I'm choosing sports books) and include the title, author(s) and two attributes of my choosing.  I will then create three separate files in teh HTML, XML, and JSON file formats and post them to my github.  Finally, I will write R code and load the three separate files from github and compare the three imported dataframes to see if they are identical.

## Pulling in the HTML code

```{r}
bookhtml <- "https://raw.githubusercontent.com/mjgons/DATA607/master/Data607Books.html"
bookhtml2 <- getURL(bookhtml)
bookhtml3 <- readHTMLTable(bookhtml2, header=TRUE)
bookhtml3

```

## Pulling in the XML code


```{r}
bookxml <- "https://raw.githubusercontent.com/mjgons/DATA607/master/Data607Books.xml"
bookxml2 <- getURL(bookxml)
bookxml3 <- xmlToDataFrame(bookxml2)
bookxml3
 


```

## Pulling in the JSON code

```{r}

bookjson <- "https://raw.githubusercontent.com/mjgons/DATA607/master/Data607Books2.json"
bookjson2 <- getURL(bookjson)
bookjson3 <- fromJSON(bookjson2)
bookjson3

```

## Conclusion

I created the 3 filetypes: HTML, XML, and JSON by hand as I've never worked with these filetypes before.  I then pushed the files to github and then pulled them into R.

The dataframes all look similar.  I have a $‘NULL‘ in the html file but other than that, they all look the same.



