---
title: "Airlines"
author: "MG"
date: "9/26/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```


## Tidying and Transforming Data
This assignment is about creating a csv file and then transforming the data to provide analysis on two airlines flight perfmance on key Western airports.

```{r}

```



## Create the .csv file

My first step was to create the data file in Excel and save it as a csv file.

https://github.com/mjgons/DATA607/blob/master/Book1.csv


```{r}

```
## Import the .csv file

I then imported the csv file into r.

```{r}
df <- read.csv("Book1.csv", header = TRUE)
head(df)

df2 <- as_tibble(df)
head(df2)

```
## Transforming the data by going from wide to long

Once the data was imported, it needed to be transformed in order to provide analysis.
I'm flipping the data from wide to long in order to do calculations easier.

```{r}
df3 <- gather(df2, "Arrival City", "Flight Count", 3:7)
  
head(df3, 10)

```
## More Transforming the data by breaking out the Delayed and On Time columns so I can do additional cauculations.



```{r}
df4 <- spread(df3, "Flight.Status", "Flight Count")

head(df4,10)
```


## I'm now going to add the total number of flighs by Arrival City and Airline and the on time rate.

```{r}

df5 <- df4 %>%
  mutate("Total Flights" = (`Delayed` + `On Time`),
         "On Time Rate" = (`On Time` / (`On Time` + `Delayed`))
    
  )

head(df5,15)

```


## By Airline Overall

Next it was time to look at the arrival delays of the two airlines by city and overall.  


Alaska Airlines Total Flights and On Time Rate
We can see that Alaska Airlines had 3,775 total flights and an on time rate of 88.8%
```{r}
#Alaska Airlines Total Flights and On Time Rate
df5 %>%
  filter(`Airline` == "Alaska") %>%
  summarise(total = sum(`Total Flights`), OnTimeRate = mean(`On Time Rate`))

```

AM West had nearly double the flights as 7,225 flights and an on time rate that was below Alaska at 82.2%.

```{r}
#AM West Total Flights and On Time Rate
df5 %>%
  filter(`Airline` == "AM West") %>%
  summarise(total = sum(`Total Flights`), OnTimeRate = mean(`On Time Rate`))
```
## By City Overall

Sorting (arrange) by city allows us to easily compare the on time rates by arrival city.  We see that Alaska had a better average on time rates in all five cities in this data set.  

```{r}

df5 %>%
  arrange(`Arrival City`)

```

## On Time Rates by Airline by City

```{r}

ggplot(data = df5) + 
  geom_point(mapping = aes(x = `Airline`, y = `On Time Rate`)) + 
  facet_wrap(~ `Arrival City`, nrow = 2) +
  labs(title = "On Time Rates by Airline by City") +
  theme_bw()




```





## Conclusion

The data clearly shows that Alaska Airlines had better on time rates at all five cities.  It's 88.8% on time rate was ahead of AM West's on time rate of 82.2%.  San Francisco had the worst on time rate overall of the five airports.   

```{r}

```