---
title: "MarkGonsalvesHW3"
author: "Mark Gonsalves"
date: "9/12/2020"
output:
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Part 1
College Majors

```{r}
library(tidyverse)
library(RCurl)
CollegeM <- getURL("https://raw.githubusercontent.com/fivethirtyeight/data/master/college-majors/majors-list.csv") 
collegeMajors <- data.frame(read.csv(text = CollegeM, header=TRUE))
head(collegeMajors)

collegeMajors %>%
  filter(str_detect(collegeMajors$Major, "STATISTICS|DATA"));
```

## Part 2

Transformation
```{r}
x <- c("bell pepper", "bilberry", "blackberry","blood orange","blueberry","cantaloupe","chili pepper", "cloudberry", "elderberry", "lime", "lychee", "mulberry", "olive", "salal berry")
x

str_c(c(x), collapse = ", ")

```
## Part 3

```{r}
x <- c("apple", "banana", "kiki", "pear","Mississippi","azzzbra", "abaca", "baba", "abba", "ababa", "abbcccddddcccbba")
```

"(.)\1\1"
This will look for a character that is the same three times in a row.  

```{r}
str_view(x,"(.)\\1\\1", match = TRUE)
```


"(.)(.)\\2\\1"
This will find where the is a character followed by a pair of characters and then the same character at the beginning.  For Mississippi, it is finding the "issi" pattern.

```{r}
str_view(x, "(.)(.)\\2\\1", match = TRUE)
```
"(..)\1"
This will look for repeated patterns like "baba".

```{r}
str_view(x, "(..)\\1", match = TRUE)
```
"(.).\\1.\\1"
This will look for a character and then another character then the 1st character again and then another character and then the first character again.
```{r}
str_view(x, "(..)\\1", match = TRUE)
```
"(.)(.)(.).*\\3\\2\\1"
This expression looks for three characters and then any in between and then the same characters in reverse order. For example, "ississi" in Mississippi.
```{r}
str_view(x, "(.)(.)(.).*\\3\\2\\1", match = TRUE)
```

## Part 4

```{r}
y <- c("apple", "banana", "kiki", "pear","Mississippi","azzzbra", "abaca", "baba", "abba", "ababa", "abbcccddddcccbba", "church", "eleven")
```


Start and end with the same character: Uses the anchors of ^ at the beginning of the string and $ at the end of the string.
```{r}
str_subset(y, "^(.)((.*\\1$)|\\1?$)")

```

Contain a repeated pair of letters: searches through the string to look whre there is a repeating pattern of combined letters such as "kiki".
```{r}
str_subset(y, "([A-Za-z][A-Za-z]).*\\1")

```

Contain one letter repeated in at least 3 places:  Searches throught the letters searching for a letter that is used 3 times.
```{r}
str_subset(y, "([a-z]).*\\1.\\1")

```
