---
title: "Gonsalves"
author: "Gonsalves"
date: "8/30/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Steak Preference in the USA

Website FiveThirtyEight published an article, <https://fivethirtyeight.com/features/how-americans-like-their-steak/> about how Americans like to eat their steak.  The article looked if risk-averse people like their steak well done, yet the author of the article was unable to find a correlation.   

```{r FiveThirtyEight Steak}
library(RCurl)
steakSurveyRawData <- getURL("https://raw.githubusercontent.com/fivethirtyeight/data/master/steak-survey/steak-risk-survey.csv") 

steakSurveyFile <- data.frame(read.csv(text = steakSurveyRawData, header=TRUE))


```

## Rename Column Names
Renaming column names to make it more legible.  

```{r rename}
colnames(steakSurveyFile) <- c("ID", "Lottery", "Smoke", "Alcohol", "Gamble", "Skydive", "Speed", "Cheat", "Eat Steak", "How Prepared", "Gender", "Age", "Income", "Education", "Region")
```

## Subset the Data Frame
Removing columns and row to focus the data.

```{r Subset}
steakSurveyReduced <- data.frame(steakSurveyFile$ID, steakSurveyFile$"Eat Steak", steakSurveyFile$"How Prepared", steakSurveyFile$Cheat, steakSurveyFile$Skydive)
steakSurveyReduced2 <- steakSurveyReduced[2:551, ] # Removed row 1 which had bad data
colnames(steakSurveyReduced2) <-c("ID", "Eat Steak", "How Prepared", "Cheat on Spouse", "Skydive") 
```

## How many people like steak?
Seeing how many eat steak.

```{r Like Steak}

summary(steakSurveyReduced2$"Eat Steak")

```
## How do people like it prepared?
Finding out how people like it prepared.

```{r Preparred}

summary(steakSurveyReduced2$"How Preparred")

```

## Conclusion

The survey data showed that 109 People didn't eat steak while 430 people did eat stak. 166 people liked their steak prepared medium rate while only 23 like it rare. I would like to revisit the study and compare it to people who like fish and see if people like their fish and steak prepared the same way.


```{r Conclusion}
summary(steakSurveyReduced2)
```



