---
title: "MarkGonsalvesAssignment2"
author: "Mark Gonsalves"
date: "9/6/2020"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Overview of Project

1) I first mocked up a survey template in Excel. 

<https://github.com/mjgons/DATA607/blob/master/.github/workflows/Movie%20Reviews%20Survey%20Template.xlsx>

2) Then I created a survey using google forms and emailed it out.
<https://docs.google.com/forms/d/e/1FAIpQLSeBOS6qeF43XUcsD6271HWFjzZ1HS7GzhfE_GMUKqI-9-y5IA/viewform?vc=0&c=0&w=1&flr=0>
The survey includes an option for "unknown" if a person hasn't watched the movie.  The survey requries a response to all questions so there won't be missing data.  

3) I exported the survey from google forms to a CSV file on my computer.
<https://github.com/mjgons/DATA607/blob/master/.github/workflows/Movie%20Reviews.csv>

4) I cleaned up the data in excel and saved it as a CSV file. 

5) I uploaded the cleaned CSV file to my GitHub account.

<https://github.com/mjgons/DATA607/blob/master/.github/workflows/Movie%20Reviews%20Clean.csv>

6) I then created the table in MySQLWorkbench and populated the table.

Everything else is in the code below:



```{r}
library(tidyverse)
library(RMySQL)
library(DBI)
```

## Importing SQL into R and working with the data

I'm connecting the SQL database to R Studio.  Looking at the data and then creating a new dataframe called db.  



```{r}
moviedb <- DBI::dbConnect(RMySQL::MySQL(), dbname = "Movies", user="root", port=3306, host='localhost', password="******")

dbListTables(moviedb)
glimpse(moviedb)

class(dbGetQuery(moviedb,"SHOW TABLES"))
dbGetQuery(moviedb, "SHOW TABLES")
dbGetQuery(moviedb, "EXPLAIN MovieSurvey")

db <-dbGetQuery(moviedb, "SELECT * FROM MovieSurvey")

colnames(db) <-c("ID", "First Name", "Last Name", "Star Wars", "Sonic", "Trolls", "Onward", "Spider-Man", "Mulan") 
head(db)


```

## Conclusion

The data shows that Becka hasn't watched Sonic.  Most people enjoyed Sonic with 1 score of 5, 1 score of 4, 2 scores of 3 and 1 score of 1.  Thus I would recommend Becka watches Sonic with her kids Josh and Justin while I do my homework.


```{r}
#install.packages("kableExtra")
library(knitr)
library(kableExtra)
kable(db[1:6,2:9 ], caption = "Movie Reviews") %>%
kable_styling(bootstrap_options = c('striped', 'hover', 'responsive', 'condensed'))
```

